CAT-DWAM, A Question Answering System

### 2011-05-07 paper/paper.tex
booktabs
fix table and stuff

\documentclass{article}

% required includes
\usepackage{graphicx}
\usepackage{url}

@@

\subsection{Other choices}
Since the system was taking too long to run we made several choices in order
to get meaningful results on which to report on. We decided to specifically analyze
the "Where" questions since there were 28 of them, which seemed like an appropriate
amount which to train on.

\section{Results}

% we need:
% the output file of answers produced by our system for the questions
% from the development corpus
% an evaluation using the Mean Reciprocal Rank Evaulation Measure)
% an analysis of the system's performance on questions of the
% development corpus
   % what worked?
   % what didn't work?
   % which component was strongest/weakest?
   % how does our system compare to the baseline?
% responses from our system for test set released on Wednesday
   % we also need to submit this file

>>>>

\documentclass{article}
\usepackage{booktabs}
% required includes
\usepackage{graphicx}
\usepackage{url}

@@

\subsection{Other choices}
Since the system was taking too long to run we made several choices in order
to get meaningful results on which to report on. We decided to specifically analyze
the ``Where'' questions since there were 28 of them, which seemed like an appropriate
amount to train on. We ran into some prombles with some of these questions, so we
actually only used 24 of these questions.

\section{Results}
\begin{table}
\begin{tabular}{lcc}
%\toprule
\cmidrule{2-3}
                     & Number correct & Mean recipricol rank\\
\cmidrule{2-3}
Punctuation location &                &                     \\
Novelty factor       &                &                     \\
Both                 &                &                     \\
\cmidrule{2-3}
%\bottomrule
\end{tabular}
%\caption{\label{tab:results}Results of our system on ``Where''-type questions. 
\end{table}
% we need:
% the output file of answers produced by our system for the questions
% from the development corpus
% an evaluation using the Mean Reciprocal Rank Evaulation Measure)
% an analysis of the system's performance on questions of the
% development corpus
   % what worked?
   % what didn't work?
   % which component was strongest/weakest?
   % how does our system compare to the baseline?
% responses from our system for test set released on Wednesday
   % we also need to submit this file
